### 2014-06-06 method.tex
changes
pixel gradient detail

To compute the pixel gradient feature, we run this CNN forward from image input to the prediction layer, then backward, all the way to the input pixels.
\todo{@sergey: waiting on evan for his prior sentences on the subject}
A couple of example pixel gradient images are shown in \autoref{fig:gradient}.

@@

\begin{table}[ht]
\centering
\caption{
    Pyramid R-CNN design choices.
}\label{tab:prcnn}
\small{
\input{pyra_rcnn_table}
}
\end{table}

>>>>

This pixel-wise gradient can be seen as a first-order approximation to the weight of a pixel in the classification output.
To compute it, we first run the CNN forward from image input to the prediction layer.
Back-propagating through the model and a last backward pass to the input gives the pixel-wise gradient.
A couple of example images are shown in \autoref{fig:gradient}.

@@

\begin{table}[ht]
\centering
\caption{
    Pyramid R-CNN design choices, vs mAP performance.
    We additionally show two best and two worst performing classes.
}\label{tab:prcnn}
\small{
\input{pyra_rcnn_table}
}
\end{table}
